% TODO:
%   o Rose mentions centrality; important for us?

\section{Introduction}

- Why forum important
    o For humanities
    o For helping each other
- Not all participate
    o why?
    o Observing actions every week to predict dropout.
      Maybe had forum actions?:
      Balakrishnan Girish. Predicting Student Retention in Massive
      Open Online Courses using Hidden MarkovModels. EECS Department,
      University of California, Berkeley, May, 2013.   

- Residential is different from MOOCs:
    o Incentives: more at stake after drop-out
    o Problem of forum cliques falling apart from
      course attrition goes away.
    o No late-comers that stay at the periphery
        (Rose:Turn-off)
    o Possible prior acquaintance
    o Smaller
- We have evidence that encouragement tricky
    o Grade: reduces intrinsic motivation.
    o Appeal to personal growth: negative
    o Appeal to community ?
    o These interventions were at the start, when
        urgency not there yet.
- Now: many courses available: reruns and varied
    o We can see dynamics of forum participation
      over time through a course. For top and
      average students.
    o When do prolific students tend to get engaged?
    o At any point in time, can we see a
      trajectory of prolific and median students?

- Analyzed the graph, snapshots over time. Are there
  inflection points?

    o Cite
      [14] Borgatti, Stephen P. Centrality and network flow. Social
      networks 27.1 (2005): 55-71. Rose uses their interpretation of
      what the social graphs mean 
    o Identify places where encouragement could be given.
      Inflection points?

    o We don't discuss the *form* of encouragement, though
      the messaging is important:

      * These say that emotional support is important:

        [13] Wang, Yi-Chia, Robert Kraut, and John M. Levine. To stay
        or leave?: the relationship of emotionaland informational support
        to commitment in online health support groups. Proceedings of the
        ACM 2012conference on Computer Supported Cooperative Work. ACM,
        2012.       
      * Could appeal to personal gain for forum participation,
      * Could appeal to community gain for forum participation,
      * Could just state facts.

\section{From Posts to Connection Graph}



